### 2017-03-06 vargo/loopStates.Rmd
Fixed bug in state loop

for(state in names(states)){

@@

    for(muNT in ntVec){
        base <- update(base, list(muNonTravel = muNT))
        for(wlk in wVec){
            for(cyc in cVec){
                scenario <- update(base, list(muwt = wlk, muct = cyc, muNonTravel = muNT))
                activityLevel <- ifelse(muNT == ntVec[1], "Low", ifelse(muNT == ntVec[2], "Medium", ifelse(muNT == ntVec[3], "High", NA)))
                comparativeRisk <- data.frame(ST = state,
                                              cycleTime = getMeans(scenario)$cycle,
                                              walkTime= getMeans(scenario)$walk,
                                              minIncreaseCycle = cyc-baseCycle,
                                              minIncreaseWalk = wlk-baseWalk,
                                              nonTravelActivity = activityLevel)

@@

@@

allStatesResults <- data.frame(allStatesResults, total = t(totalDALYs))

@@

>>>>

stateVec <- names(states)

for(state in stateVec){

@@

    for(muNT in ntVec){
        base <- update(base, list(muNonTravel = muNT))
        for(wlk in wVec){
            for(cyc in cVec){
                scenario <- update(base, list(muwt = wlk, muct = cyc, muNonTravel = muNT))
                activityLevel <- ifelse(muNT == ntVec[1], "Low", ifelse(muNT == ntVec[2], "Medium", ifelse(muNT == ntVec[3], "High", NA)))
                comparativeRisk <- data.frame(ST = state,
                                              cycleTime = getMeans(scenario)$cycle,
                                              walkTime= getMeans(scenario)$walk,
                                              minIncreaseCycle = cyc-baseCycle,
                                              minIncreaseWalk = wlk-baseWalk,
                                              nonTravelActivity = activityLevel, stringsAsFactors = FALSE)

@@

                foo <- data.frame(foo, total = t(totalDALYs))

@@

summary(allStatesResults)

@@

summary(allStatesResults)
